Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-14 tex/MISDP-Presolving/MISDPpresolving.tex
extend section about bounds for rank-1 motivated structures

\begin{remark}
  Most likely this can be generalized to the more interesting case of a
  constraint of the form
  \[
  \begin{pmatrix}
    t & x\T \\
    x & X
  \end{pmatrix}
  \succeq 0,
  \quad
  \ell \leq (x,t) \leq u,
\]
where~$t$ is a scalar variable. Since constraints of this particular form
appear in truss topology design and cardinality least-squares problems, we
should check whether this helps for such instances.
\end{remark}

>>>>

\begin{remark}
  This can be generalized to the more interesting case of a
  constraint of the form
  \[
  \begin{pmatrix}
    t & x\T \\
    x & X
  \end{pmatrix}
  \succeq 0,
  \quad
  \ell \leq x \leq u,\quad \ell_t \leq t \leq u_t,
\]
where~$t$ is a scalar variable. Constraints of this particular form
appear, e.g., in truss topology design and cardinality least-squares
problems. The same argument as above yields the two inequalities
\begin{align*}
  X_{ii} &\geq \frac{2 \ell_i x_i - \ell_i^2}{u_t} \\
  X_{ii} &\geq \frac{2 u_i x_i - u_i^2}{u_t}
\end{align*}
Assume that~$\ell_i < 0$ and ~$u_i > 0$. Then, these inequalities can be
non-trivial, that is, the right-hand-side is nonnegative,
if~$x_i \leq \ell_i/2$ and~$x_i \geq u_i/2$, respectively. Additionally, by
replacing~$x_i$ by its lower bound~$\ell_i$, the first inequality can be
used for propagation:
\begin{align*}
  X_{ii} &\geq \frac{2 \ell_i u_i - \ell_i^2}{u_t},
\end{align*}
where the right-hand-side is strictly positive, if $\ell_i > u_i/2$, $u_t >
0$ and either~$u_i > 0$ or~$\ell_i$, $u_i < 0$.

These inequalities are currently not implemented, but it may be worth
testing them on different types of problems with LP- or SDP-solving to see
if they have any impact.
\end{remark}
